Reading Notes

### 2020-08-27 2pd.tex
fix very strange errors with chktex and autoref

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}\label{opv}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b -- d) adapted from ref~\cite{Miller2018c}.} % chktex 8
\end{wrapfigure}

The global climate crisis is one of the most pressing issues humanity faces today.
Consumption of fossil fuels for energy and transportation strongly contributes to rising atmospheric $CO_{2}$ levels the effects of which are global, long-term, and devastating\cite{Solomon2009a}.
In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in \autoref{opv} a\cite{Dou2013}.
However, other materials still outperform OPVs (see \autoref{nrel}), and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{images/NREL2020.pdf}\label{nrel}
    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present. The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}. Data taken from~\cite{NREL2020}.}
\end{figure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/chem_structures.pdf}\label{chemistries}
    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/ITIC.pdf}\label{itic}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}
\end{wrapfigure}

@@

MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).
\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}\label{bad}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}
\end{wrapfigure}
Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
\[
    U_{LJ}(r_{i,j}) = 4\epsilon\big[
        {\big(\frac{\sigma}{r_{i,j}}\big)}^{12}-
        {\big(\frac{\sigma}{r_{i,j}}\big)}^{6}
        \big]
\]
Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see \autoref{lj}).
A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/lj.pdf}\label{lj}
    \caption{The Lennard-Jones potential with relevant distances labelled}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/moorefig.pdf}\label{moore}
    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target. Choosing states which are different (a) will better define the potential. Image adapted from ref~\cite{Moore2014}.}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}\label{hexane}
    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}
\end{wrapfigure}

@@

It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse-grained sites (A-B-A), that the process will also be simple.
In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
To explain, let's discuss my proposed alternative:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA\cite{grits}.
The mapping here is specified as a list of site name SMARTS string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}). % chktex 18
The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first. % chktex 18
The bonding and angles of the resulting coarse-grained sites can then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
(\autoref{hexane} is the output of one such visualization using py3Dmol\cite{py3dmol}.)

@@

In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to estimate the atomic positions.
Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse-graining.
The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure. 
This method is not fundamentally different from many existing backmapping routines in that the atomistic structure is naively positioned over the coarse site and then relaxed --- the main difference lies in the amount of additional work required from the user\cite{Wassenar2014b, MorphCT, Ruhle2009}.
Since the user has already specified the mapping to go from atomistic to coarse, it can be reused for backmapping.
The bonding between the atomistic structures of the sites is lost, so this information will need to be provided: either specified by the user or recorded during the coarse graining step.
I have developed a minimum working example of this backmapping process\cite{grits},
however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I have yet to implement automated tracking of the conds during the coarse graining.

@@

\section*{Timeline for Implementation and Evaluation}
\begin{table}[h]
    \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|} % chktex 44
        \hline % chktex 44
        \multirow{2}{*}{PROJECT TASK}
            &\multicolumn{4}{c}{YEAR 1}
            &\multicolumn{4}{|c}{YEAR 2} 
            &\multicolumn{4}{|c}{YEAR 3} 
            &\multicolumn{4}{|c|}{YEAR 4} 
            &\multicolumn{4}{c|}{YEAR 5} \\ 
        \hhline{~--------------------}
        & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
        \hline % chktex 44
        Complete Coursework 
            &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
        \hline % chktex 44
        Present at a Conference  
            & & & & & & & & & & & x & & & & & & & & &\\
        \hline % chktex 44
        Publish a First Author Paper
            & & & & & & x & & & & & & & & & & & & & &\\
        \hline % chktex 44
        Proposal and Comprehensive Exam
            & & & & & & & & & & & & * & & & & & & & &\\
        \hline % chktex 44
        Expand Functionality of Open Source Packages 
            & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline % chktex 44
        Develop Coarse Graining Package              
            & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline % chktex 44
        Develop Automated MS-IBI Code                
            & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline % chktex 44
        Develop Backmapping Package                  
            & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
        \hline % chktex 44
        Generate Coarse-Grain Morphologies           
            & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
        \hline % chktex 44
        Evaluate OPV Device Performance 
            & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
        \hline % chktex 44
        Write Dissertation 
            & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
        \hline % chktex 44
        Present Dissertation Defense  
            & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
        \hline % chktex 44
         %Saved row template
         %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
        \end{tabular}
    }
    \caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
\end{table}

>>>>

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{Schematic showing (a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
\end{wrapfigure}

The global climate crisis is one of the most pressing issues humanity faces today.
Consumption of fossil fuels for energy and transportation strongly contributes to rising atmospheric $CO_{2}$ levels the effects of which are global, long-term, and devastating\cite{Solomon2009a}.
In our technology-driven society, it is unrealistic to think that energy demand will lessen, in fact global energy consumption is predicted to increase from 17 TW in 2010 to 27 TW in 2040\cite{Mazzio2015}.
In order to protect our climate, we need a non-polluting, cost-efficient way to provide electricity.
Harnessing solar energy is an important part of a green energy solution.
Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.
Traditionally, photovoltaic (PV) devices, which can convert incedent light into electric current, were made of inorganic materials like silicon.
But in the late 1970's organic photovaltaics (OPVs) were discovered as a potential alternative\cite{Tang1986b}.
The advantage of OPVs over inorganic PV devices is that OPVs are lightweight, low cost, easier to produce, and flexible. 
OPVs can be manufactured large scale in a roll to roll printing process, similar to newspaper, as shown in~\autoref{opv} a\cite{Dou2013}.
However, other materials still outperform OPVs (see \autoref{nrel}), and in order to become a viable, cost-effective option OPVs need to be more efficient\cite{Mazzio2015}.

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{images/NREL2020.pdf}
    \caption{Comparision of efficiencies organic and silicon photovoltaic technologies from 1990 to present. The current state-of-the-art OPV, polymer-fullerene device coupled with transition metal disulfide, achieves 17.4\% efficiency\cite{Lin2019}. Data taken from~\cite{NREL2020}.}\label{nrel}
\end{figure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/chem_structures.pdf}
    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}\label{chemistries}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/ITIC.pdf}
    \caption{ITIC chemical structure with \textcolor{red}{electron accepting regions in red} and \textcolor{blue}{electron donating regions in blue}}\label{itic}
\end{wrapfigure}

@@

MD separates the interactions between particles into non-bonded interactions and bond, angle, and dihedral interactions (see \autoref{bad}).
\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/bondangledihedral.pdf}
    \caption{Bonded interactions: bond (top left), angle (top right), and dihedral (bottom). Image adapted from~\cite{punma}.}\label{bad}
\end{wrapfigure}
Non-bonded interactions are commonly modelled with a Lennard-Jones potential:
\[
    U_{LJ}(r_{i,j}) = 4\epsilon\big[
        {\big(\frac{\sigma}{r_{i,j}}\big)}^{12}-
        {\big(\frac{\sigma}{r_{i,j}}\big)}^{6}
        \big]
\]
Where $i$ and $j$ are the particles separated by distance $r_{i,j}$.
The equilibrium distance between particles is controlled by $\sigma$ and the depth of the potential well is controlled by $\epsilon$ (see \autoref{lj}).
A distance cutoff, $r_{cut}$, is often used to reduce the number of pairwise interactions and improve performance.

\begin{wrapfigure}{L}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/lj.pdf}
    \caption{The Lennard-Jones potential with relevant distances labelled}\label{lj}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/moorefig.pdf}
    \caption{Visualization of the state space coverage of different potentials: if the thermodynamic states are too similar (b), then the overlap region is large enough that there are many potentials which will fit the target. Choosing states which are different (a) will better define the potential. Image adapted from ref~\cite{Moore2014}.}\label{moore}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/hexane-compare.pdf}
    \caption{Hexane chemical structure (top) overlaid with coarse-grained mapping \textcolor{blue}{A}-\textcolor{orange}{B}-\textcolor{blue}{A} (bottom)}\label{hexane}
\end{wrapfigure}

@@

It may be easy to think that because the goal is simple, mapping two carbons and their attached hydrogens to a single site so that six alkyl carbons becomes three coarse-grained sites (A-B-A), that the process will also be simple.
In order to specify a site-mapping using VOTCA, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but it could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is coarse grained or  backmapped.
VOTCA's scheme also requires that the bonding and the angles resulting from those bonds are specified, another process which is tedious, error-prone, and probably unecessary. 
To explain, let's discuss my proposed alternative:
\begin{lstlisting}
hexane_sites = [("_A", "C[CH3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the \lstinline{coarse} function is a three-site hexane model A-B-A, same as VOTCA\cite{grits}.
The mapping here is specified as a list of site name SMARTS string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (in SMARTS notation a capital \lstinline{"C"} denotes an alkyl carbon) and requiring that one be a terminal carbon by including that it has three attached hydrogens (\lstinline{"[CH3]"}).
The order of the sites here matters because technically all the carbon atoms in hexane could be mapped with the more general SMARTS string (\lstinline{"CC"}), so it is important to list the most specific strings first.
The bonding and angles of the resulting coarse-grained sites can then inferred based on the bonding of the mapped atoms.
Basically what VOTCA's xml file does in 51 lines, I can do in 1 which is easier to read and makes chemical sense. 
There are even benefits to the mapping being inline with the code:
It allows the user to see the mapping as they progress through the workflow without having to search for multiple files.
Not using an external file may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being read differently by a program.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay. 
(\autoref{hexane} is the output of one such visualization using py3Dmol\cite{py3dmol}.)

@@

In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to estimate the atomic positions.
Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse-graining.
The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure. 
This method is not fundamentally different from many existing backmapping routines in that the atomistic structure is naively positioned over the coarse site and then relaxed --- the main difference lies in the amount of additional work required from the user\cite{Wassenaar2014b, MorphCT, Ruhle2009}.
Since the user has already specified the mapping to go from atomistic to coarse, it can be reused for backmapping.
The bonding between the atomistic structures of the sites is lost, so this information will need to be provided: either specified by the user or recorded during the coarse graining step.
I have developed a minimum working example of this backmapping process\cite{grits},
however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I have yet to implement automated tracking of the conds during the coarse graining.

@@

\section*{Timeline for Implementation and Evaluation}
\begin{table}[h]
    \resizebox{\columnwidth}{!}{\renewcommand{\arraystretch}{1.1}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
        \hline
        \multirow{2}{*}{PROJECT TASK}
            &\multicolumn{4}{c}{YEAR 1}
            &\multicolumn{4}{|c}{YEAR 2} 
            &\multicolumn{4}{|c}{YEAR 3} 
            &\multicolumn{4}{|c|}{YEAR 4} 
            &\multicolumn{4}{c|}{YEAR 5} \\ 
        \hhline{~--------------------}
        & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
        \hline
        Complete Coursework 
            &\multicolumn{10}{|c|}{{\cellcolor{lgray}}} &  &  &  &  &  &  &  &  &  &\\
        \hline
        Present at a Conference  
            & & & & & & & & & & & x & & & & & & & & &\\
        \hline
        Publish a First Author Paper
            & & & & & & x & & & & & & & & & & & & & &\\
        \hline
        Proposal and Comprehensive Exam
            & & & & & & & & & & & & * & & & & & & & &\\
        \hline
        Expand Functionality of Open Source Packages 
            & & & & & & \multicolumn{11}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
        Develop Coarse Graining Package              
            & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
        Develop Automated MS-IBI Code                
            & & & & & & & & & \multicolumn{8}{|c|}{{\cellcolor{lgray}}} & & & &\\
        \hline
        Develop Backmapping Package                  
            & & & & & & & & & & & & \multicolumn{5}{|c|}{{\cellcolor{lgray}}}& & & &\\
        \hline
        Generate Coarse-Grain Morphologies           
            & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}}& & &\\
        \hline
        Evaluate OPV Device Performance 
            & & & & & & & & & & & & & & \multicolumn{4}{|c|}{{\cellcolor{lgray}}} & & &\\
        \hline
        Write Dissertation 
            & & & & & & & & & & & & & & & &\multicolumn{3}{|c|}{{\cellcolor{lgray}}} & &\\
        \hline
        Present Dissertation Defense  
            & & & & & & & & & & & & & & & & & & {\cellcolor{lgray}} &  &\\
        \hline
         %Saved row template
         %&  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  \\
        \end{tabular}
    }
    \caption{Anticipated timeline. * indicates right now, x indicates already accomplished.}
\end{table}
